---
title: "pj2"
author: '620'
date: "4/10/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)
library(ggplot2)
library(tidyverse)
```

```{r}
df_sc= read_xlsx('rawdata/620W22-Project2-Data.xlsx',sheet = 1)
df_bs= read_xlsx('rawdata/620W22-Project2-Data.xlsx',sheet = 2)
df_bs =df_bs[,1:14]
df_sc['LOAD'] = df_sc$Tot.Soc.Time/df_sc$Tot.Scr.Time
df_sc['DUR'] = df_sc$Tot.Scr.Time/df_sc$Pickups
```

# generate the baseline/intervention phase
```{r}
df_sc = df_sc %>% mutate(phase = case_when(
  Time <= 15 ~ 'baseline',
  Time<=23 ~'A',
  Time <= 30 ~ 'B'
))
```

# check  the data quality 
the total screen time should be greater than social screen time
```{r}
sum(df_sc$Tot.Scr.Time < df_sc$Tot.Soc.Time, na.rm = T)
df_sc[df_sc$Tot.Scr.Time < df_sc$Tot.Soc.Time,]
df_sc[(df_sc$ID == 25 & df_sc$Time ==13),'Tot.Scr.Time'] = 207
df_sc[(df_sc$ID == 25 & df_sc$Time ==13),'Tot.Soc.Time'] = 164
```

# convert the first pickup time into a numeric data
```{r}
df_sc$first_pk = unlist(lapply(df_sc[['Pickup.1st']],function(x) as.numeric(strsplit(x, ':')[[1]][1])*60 + 
                          as.numeric(strsplit(x, ':')[[1]][2]) ))
```


# generate the average values of outcomes grouped by the ID and phase 
as for the missing data, we can conduct the robust analysis.
```{r}
df_sc = df_sc %>% group_by(ID, phase ) %>% mutate(avg_scr = mean(Tot.Scr.Time, na.rm = T),
                                                   avg_soc = mean(Tot.Soc.Time, na.rm = T),
                                                   avg_pk = mean(Pickups, na.rm = T),
                                                  avg_firstpk = mean(first_pk, na.rm = T),
                                                   avg_load = mean(LOAD, na.rm = T),
                                                   avg_dur = mean(DUR, na.rm = T)
                                                   )
```

#
```{r}
pre_avg = df_sc %>%group_by(ID) %>% filter(phase == 'baseline') %>% summarise(total_soc_mean = mean(Tot.Soc.Time)) %>% mutate(phase = 'P')
post_avg_A = df_sc %>%group_by(ID) %>% filter(phase == 'A') %>% summarise(total_soc_mean= mean(Tot.Soc.Time)) %>% mutate(phase = 'A')
post_avg_B = df_sc %>%group_by(ID) %>% filter(phase == 'B') %>% summarise(total_soc_mean = mean(Tot.Soc.Time,na.rm = T)) %>% mutate(phase = 'B')
# post_avg_E = df_sc %>%group_by(ID) %>% filter(phase == 'E') %>% summarise(total_soc_mean = mean(Tot.Soc.Time)) %>% mutate(phase = 'E')


pre_post_diff = data.frame(ID = post_avg_A$ID,
                           A = post_avg_A$total_soc_mean-pre_avg$total_soc_mean,
                           B= post_avg_B$total_soc_mean-pre_avg$total_soc_mean
)
```


# merge pre_post_diff with baseline table
```{r}
data = full_join(pre_post_diff,df_bs, by = "ID")
head(data)
```
# pivot the columns
```{r}
data = data[ complete.cases(data),]
data = data %>% pivot_longer(c('A','B'),names_to ='phase', values_to = 'diff')
data = data[complete.cases(data),]
data
```
## model A

```{r}
df1 = data%>% filter(phase =='A') 
df1 =df1[-c(1,15)]
df1 = df1[-c(1:3)]

df2 = data%>% filter(phase =='B')
df2= df2[-c(1,15)]

library(MASS)
df1$age = df1$age -23
df1$devices = df1$devices -2
df1$procrastination = df1$procrastination-35.50
df1$course.hours = df1$course.hours-13
df1$apps = df1$apps - 4

fitA = lm(diff ~ .+sex:procrastination, data= df1)
stepaicA = stepAIC(fitA,scope =list(lower = ~ sex + procrastination +age+ apps+ sex:procrastination, upper = fitA), trace =FALSE)
summary(stepaicA )

procas =12:68 - 35.5
sex = c(0,1)
age = 21:30 -23
pro_sex =merge(data.frame(procrastination = procas), data.frame(sex = sex), by = NULL)
pro_sex['age'] = 0
age_sex = merge(data.frame(age = age), data.frame(sex = sex), by = NULL)
age_sex['procrastination'] = 35.5

pre = predict(stepaicA,pro_sex, interval = 'confidence',se.fit = T)
value = pre$fit
se = pre$se.fit
pro_sex = cbind(pro_sex, value,se)
pro_sex['z'] = pro_sex$fit /pro_sex$se
pro_sex['pvalue'] = pt(abs(pro_sex$z), df = 27,lower.tail = FALSE) *2


pre2 = predict(stepaicA,age_sex, interval = 'confidence',se.fit = T)
value = pre2$fit
se = pre2$se.fit
age_sex = cbind(age_sex, value,se)
age_sex['z'] = age_sex$fit /age_sex$se
age_sex['pvalue'] = pt(abs(age_sex$z), df = 27,lower.tail = FALSE) *2



```


```{r}
library(ggplot2)
pro_sex$sex = as.factor(pro_sex$sex)
pro_sex %>% ggplot(aes(x = procrastination+35.5,y = fit,group = sex)) + geom_line(aes(color = sex)) + geom_ribbon(aes(ymin = lwr,ymax = upr, fill = sex), alpha = 0.2,linetype=2) + ylab('Pre-post Difference of Total Social Screen Time') + xlab("Procrastination value")+ggtitle('Adjusting for the median age (23)')+theme(plot.title = element_text(hjust = 0.5))
```


```{r}
age_sex$sex = as.factor(age_sex$sex)
age_sex %>% ggplot(aes(x = age+23,y = fit,group = sex)) + geom_line(aes(color = sex)) + geom_ribbon(aes(ymin = lwr,ymax = upr, fill = sex), alpha = 0.2,linetype=2) + ylab('Pre-post Difference of Total Social Screen Time') + xlab("Age") + ggtitle('Adjusting for the median procrastination score (35.5)')+theme(plot.title = element_text(hjust = 0.5))
```





```{r}
df2$age = df2$age -23
df2$devices = df2$devices -2
df2$procrastination = df2$procrastination-35.50
df2$course.hours = df2$course.hours-13
df2$apps = df2$apps - 4
df3 = df2[-c(1:3)]
fitB = lm(diff ~ sex*(.), data= df3)
stepaicB = stepAIC(fitB,scope =list(lower = ~ sex + procrastination +age+sex:procrastination, upper = fitB), trace =FALSE)
summary(stepaicB)

fitB2 = lm(diff~ sex + age + degree + apps + procrastination+sex:procrastination, data = df3)
summary(fitB2)
```

```{r}
apps =1:32 - 4
sex = c(0,1)
age = 21:30 -23
apps_sex =merge(data.frame(apps= apps), data.frame(sex = sex), by = NULL)
apps_sex['age'] = 0
apps_sex['procrastination'] = 0
apps_sex['degree'] = 0

pre = predict(fitB2,apps_sex, interval = 'confidence',se.fit = T)
value = pre$fit
se = pre$se.fit
apps_sex = cbind(apps_sex, value,se)
apps_sex['z'] = apps_sex$fit /apps_sex$se
apps_sex['pvalue'] = pt(abs(apps_sex$z), df = 27,lower.tail = FALSE) *2
```

```{r}
apps_sex$sex = as.factor(apps_sex$sex)
apps_sex %>% ggplot(aes(x = apps+4,y = fit,group = sex)) + geom_line(aes(color = sex)) + geom_ribbon(aes(ymin = lwr,ymax = upr, fill = sex), alpha = 0.2,linetype=2) + ylab('Pre-post Difference of Total Social Screen Time') + xlab("The amount of apps")+ggtitle('Adjusting for the median age (23),median procrastination(35.5), \nand Non-US degree ')+theme(plot.title = element_text(hjust = 0.5))
```

```{r}
apps =1:32 - 4
deg = c(0,1)
age = 21:30 -23
apps_deg =merge(data.frame(apps= apps), data.frame(degree = deg), by = NULL)
apps_deg['sex'] = 0
apps_deg['procrastination'] = 0
apps_deg['age'] = 0

pre = predict(fitB2,apps_deg, interval = 'confidence',se.fit = T)
value = pre$fit
se = pre$se.fit
apps_deg = cbind(apps_deg, value,se)
apps_deg['z'] = apps_deg$fit /apps_deg$se
apps_deg['pvalue'] = pt(abs(apps_deg$z), df = 27,lower.tail = FALSE) *2
```

```{r}
apps_deg$degree = as.factor(apps_deg$degree)
apps_deg %>% ggplot(aes(x = apps+4,y = fit,group = degree)) + geom_line(aes(color = degree)) + geom_ribbon(aes(ymin = lwr,ymax = upr, fill = degree), alpha = 0.2,linetype=2) + ylab('Pre-post Difference of Total Social Screen Time') + xlab("The amount of apps")+ggtitle('Adjusting for the median age (23),median procrastination(35.5), \nand female ')+theme(plot.title = element_text(hjust = 0.5))
```

```{r}
procas =12:68 - 35.5
sex = c(0,1)
pro_sex =merge(data.frame(procrastination = procas), data.frame(sex = sex), by = NULL)
pro_sex['apps'] = 0
pro_sex['degree'] = 0
pro_sex['age'] = 0

pre = predict(stepaicA,pro_sex, interval = 'confidence',se.fit = T)
value = pre$fit
se = pre$se.fit
pro_sex = cbind(pro_sex, value,se)
pro_sex['z'] = pro_sex$fit /pro_sex$se
pro_sex['pvalue'] = pt(abs(pro_sex$z), df = 27,lower.tail = FALSE) *2
pro_sex$sex = as.factor(pro_sex$sex)
pro_sex %>% ggplot(aes(x = procrastination+35.5,y = fit,group = sex)) + geom_line(aes(color = sex)) + geom_ribbon(aes(ymin = lwr,ymax = upr, fill = sex), alpha = 0.2,linetype=2) + ylab('Pre-post Difference of Total Social Screen Time') + xlab("Procrastination value")+ggtitle('Adjusting for the median age (23), the median number of apps,\n and Non-US degree')+theme(plot.title = element_text(hjust = 0.5))
```



# model

$$\begin{aligned}
Y_i = \beta_1I(treatment = A) + \beta_2I(treatment = B) + \beta_3I(treatment =E) + \beta_4x_{1i}+\beta_5x_{2i}+....
\end{aligned}$$

```{r}
fit1 = lm(diff~ -1+.,data= data)
summary(fit1)
```
```{r}
library(MASS)
step.aic = stepAIC(fit1,direction = 'both')
```

```{r}
fit3 = stepAIC(fit1,scope = list(lower = ~-1+phase,upper = fit1),trace =FALSE)
summary(fit3)
```
```{r}
fit4 = lm(diff~ -1+phase*(.),data= data)
fit5 = stepAIC(fit4,scope = list(lower = ~-1+phase,upper = fit4),trace =FALSE)
summary(fit5)
```
```{r}
fit6 = lm(diff~ -1+ phase*apps + workmate + academic + non.academic + 
    sex + course.hours + apps + procrastination,data= data)
summary(fit6)
```

