---
title: "620proj 2"
author: "Xin Luo"
date: "2022/4/10"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
Sys.setenv(LANG = "en")
```

```{r}
setwd('rawdata/')
```

```{r}
library(readxl)
library(ggplot2)
library(tidyverse)
library(systemfit)
```

```{r}
df_sc= read_xlsx('rawdata/620W22-Project2-Data.xlsx',sheet = 1)
df_bs= read_xlsx('620W22_Project2_Data.xlsx',sheet = 2)
df_bs =df_bs[,1:14]
df_sc['LOAD'] = df_sc$Tot.Soc.Time/df_sc$Tot.Scr.Time
df_sc['DUR'] = df_sc$Tot.Scr.Time/df_sc$Pickups
```

# generate the baseline/intervention phase
```{r}
df_sc = df_sc %>% mutate(phase = case_when(
  Time <= 15 ~ 'baseline',
  Time<=23 ~'A',
  Time <= 30 ~ 'B'
))
```

# check  the data quality 
the total screen time should be greater than social screen time
```{r}
sum(df_sc$Tot.Scr.Time < df_sc$Tot.Soc.Time, na.rm = T)
df_sc[df_sc$Tot.Scr.Time < df_sc$Tot.Soc.Time,]
df_sc[(df_sc$ID == 25 & df_sc$Time ==13),'Tot.Scr.Time'] = 207
df_sc[(df_sc$ID == 25 & df_sc$Time ==13),'Tot.Soc.Time'] = 164
```

# convert the first pickup time into a numeric data
```{r}
df_sc$first_pk = unlist(lapply(df_sc[['Pickup.1st']],function(x) as.numeric(strsplit(x, ':')[[1]][1])*60 + 
                          as.numeric(strsplit(x, ':')[[1]][2]) ))
```


# generate the average values of outcomes grouped by the ID and phase 
as for the missing data, we can conduct the robust analysis.
```{r}
df_sc = df_sc %>% group_by(ID, phase ) %>% mutate(avg_scr = mean(Tot.Scr.Time, na.rm = T),
                                                   avg_soc = mean(Tot.Soc.Time, na.rm = T),
                                                   avg_pk = mean(Pickups, na.rm = T),
                                                  avg_firstpk = mean(first_pk, na.rm = T),
                                                   avg_load = mean(LOAD, na.rm = T),
                                                   avg_dur = mean(DUR, na.rm = T)
                                                   )
```

#
```{r}
pre_avg = df_sc %>%group_by(ID) %>% filter(phase == 'baseline') %>% summarise(total_soc_mean = mean(Tot.Soc.Time)) %>% mutate(phase = 'P')
post_avg_A = df_sc %>%group_by(ID) %>% filter(phase == 'A') %>% summarise(total_soc_mean= mean(Tot.Soc.Time)) %>% mutate(phase = 'A')
post_avg_B = df_sc %>%group_by(ID) %>% filter(phase == 'B') %>% summarise(total_soc_mean = mean(Tot.Soc.Time,na.rm = T)) %>% mutate(phase = 'B')


pre_post_diff = data.frame(ID = post_avg_A$ID,
                           A = post_avg_A$total_soc_mean-pre_avg$total_soc_mean,
                           B= post_avg_B$total_soc_mean-pre_avg$total_soc_mean)
                      
```


# merge pre_post_diff with baseline table
```{r}
data = full_join(pre_post_diff,df_bs, by = "ID")
head(data)
```
# pivot the columns
```{r}
data = data %>% pivot_longer(c('A','B'),names_to ='phase', values_to = 'diff')
```

# Baseline data preprocessing and normalization
```{r}
# missing value imputation
data$age[is.na(data$age)] = median(data$age[!is.na(data$age)])
data$age_centered = data$age - median(data$age) # 23
data$apps = data$apps -median(data$apps) #4
data$course_centered = data$course.hours - median(data$course.hours) # 13
#data$apps_log = log(data$apps)
# data$procrastination_norm = (data$procrastination - mean(data$procrastination))/sd(data$procrastination)
data$procrastination = data$procrastination - median(data$procrastination) # 34.5
#data$phase_1 = 0
#data$phase_2 = 0
#data$phase_3 = 0
#data$phase_1[data$phase == 'A'] = 1
#data$phase_2[data$phase == 'B'] = 1
#data$phase_3[data$phase == 'E'] = 1
```



# SUR model

$$\begin{aligned}
Two \ regression \ models \ are \ built:
\\
Y_{1i} = \beta_{10} + \beta_{11}sex + \beta_{12}procrastination\_norm + \epsilon_{1i}
\\
Y_{2i} = \beta_{20} + \beta_{21}sex + \beta_{22}procrastination\_norm + \epsilon_{2i}
\\
Then \ seemingly \ unrelated \ regression \ model \ is \ built:


\end{aligned}$$


```{r}
data1 = subset(data, select = -c(ID, age, course.hours))
data11 = data1[data1$phase=='A',]
data12 = data1[data1$phase=='B',]
data11$diffA = data11$diff
data11$diffB = data12$diff
data11 = subset(data11, select = -c(diff, phase))
lm1 <- diffA ~ sex + age_centered + apps+procrastination+ procrastination:sex
lm2 <- diffB ~ sex + age_centered + apps +degree+procrastination+ procrastination:sex
eqSystem = list(trA = lm1, trB = lm2)
fit = systemfit(eqSystem, data = data11, method = "SUR")
summary(fit)
print(fit)
```
```{r}
#model1
# apps_sex
apps =1:32 - 4
sex = c(0,1)
age = 21:30 -23
apps_sex =merge(data.frame(apps= apps), data.frame(sex = sex), by = NULL)
apps_sex['age_centered'] = 0
apps_sex['procrastination'] = 0
apps_sex['degree'] = 0

pre = predict(fit,apps_sex, interval = 'confidence',se.fit = T)
fit_conint = pre[c("trA.pred", "trA.se.fit","trA.lwr","trA.upr")]

apps_sex = cbind(apps_sex, fit_conint)
apps_sex['z'] = apps_sex$trA.pred /apps_sex$trA.se.fit
apps_sex['pvalue'] = pt(abs(apps_sex$z), df = 27,lower.tail = FALSE) *2
apps_sex$sex = as.factor(apps_sex$sex)
apps_sex$sex = ifelse(apps_sex$sex ==0, 'Female','Male')
plt1 = apps_sex %>% ggplot(aes(x = apps+4,y = trA.pred,group = sex)) + geom_line(aes(color = sex)) + geom_ribbon(aes(ymin = trA.lwr,ymax = trA.upr, fill = sex), alpha = 0.2,linetype=2) + ylab('Pre-post Difference of\n Total Social Screen Time') + xlab("The amount of apps")+ggtitle('The effect of intervention A, \nadjusting for the median age (23) and median procrastination score(34.5) ')+theme(plot.title = element_text(hjust = 0.5))+geom_hline(yintercept=0, linetype="dashed", 
                color = "blue", size=1)
```

```{r}
# model 1
procas =12:68 - 34.5
sex = c(0,1)
pro_sex =merge(data.frame(procrastination = procas), data.frame(sex = sex), by = NULL)
pro_sex['apps'] = 0
pro_sex['degree'] = 0
pro_sex['age_centered'] = 0

pre = predict(fit,pro_sex, interval = 'confidence',se.fit = T)
fit_conint = pre[c("trA.pred", "trA.se.fit","trA.lwr","trA.upr")]

pro_sex = cbind(pro_sex, fit_conint)
pro_sex['z'] = pro_sex$trA.pred /pro_sex$trA.se.fit
pro_sex['pvalue'] = pt(abs(pro_sex$z), df = 27,lower.tail = FALSE) *2
pro_sex$sex = as.factor(pro_sex$sex)
pro_sex$sex = ifelse(pro_sex$sex ==0, 'Female','Male')
plt2= pro_sex %>% ggplot(aes(x = procrastination+34.5,y =trA.pred,group = sex)) + geom_line(aes(color = sex)) + geom_ribbon(aes(ymin = trA.lwr,ymax =trA.upr, fill = sex), alpha = 0.2,linetype=2) + ylab('Pre-post Difference of\n Total Social Screen Time') + xlab("Procrastination value")+ggtitle('The effect of intervention A, \nadjusting for the median age (23) and the median number of apps (4)')+theme(plot.title = element_text(hjust = 0.5))+geom_hline(yintercept=0, linetype="dashed", 
                color = "blue", size=1)
```

```{r}
# model1
procas =12:68 - 34.5
sex = c(0,1)
age = 21:30 -23
age_sex = merge(data.frame(age_centered = age), data.frame(sex = sex), by = NULL)
age_sex['procrastination'] = 0
age_sex['degree'] = 0
age_sex['apps'] = 0

pre = predict(fit,age_sex, interval = 'confidence',se.fit = T)
fit_conint = pre[c("trA.pred", "trA.se.fit","trA.lwr","trA.upr")]

age_sex = cbind(age_sex, fit_conint)
age_sex['z'] = age_sex$trA.pred /age_sex$trA.se.fit
age_sex['pvalue'] = pt(abs(age_sex$z), df = 27,lower.tail = FALSE) *2
age_sex$sex = as.factor(age_sex$sex)
age_sex$sex = ifelse(age_sex$sex ==0, 'Female','Male')

plt3 = age_sex %>% ggplot(aes(x =age_centered+23,y =trA.pred,group = sex)) + geom_line(aes(color = sex)) + geom_ribbon(aes(ymin = trA.lwr,ymax =trA.upr, fill = sex), alpha = 0.2,linetype=2) + ylab('Pre-post Difference of\n Total Social Screen Time') + xlab("Procrastination value")+ggtitle('The effect of intervention A,\nadjusting for the median number of apps (4),and median procrastination (34.5)')+theme(plot.title = element_text(hjust = 0.5))+geom_hline(yintercept=0, linetype="dashed", 
                color = "blue", size=1)

```

```{r}
library(ggpubr)
ggarrange(plt1,plt2,plt3,labels = c('A','B','C'),ncol =2, nrow=2)
```




```{r}
# model 2
# plot the numbers of apps and  degree
apps =1:32 - 4
deg = c(0,1)
apps_deg =merge(data.frame(apps= apps), data.frame(degree = deg), by = NULL)
apps_deg['sex'] = 0
apps_deg['procrastination'] = 0
apps_deg['age_centered'] = 0

pre = predict(fit,apps_deg, interval = 'confidence',se.fit = T)

fit_conint = pre[c("trB.pred", "trB.se.fit","trB.lwr","trB.upr")]

apps_deg = cbind(apps_deg, fit_conint)
apps_deg['z'] = apps_deg$trB.pred /apps_deg$trB.se.fit
apps_deg['pvalue'] = pt(abs(apps_deg$z), df = 27,lower.tail = FALSE) *2


# plot 
apps_deg$degree = as.factor(apps_deg$degree)
apps_deg$degree  = ifelse(apps_deg$degree  ==0, 'Non-US','uS')

plt4 = apps_deg %>% ggplot(aes(x = apps+4,y = trB.pred ,group = degree)) + geom_line(aes(color = degree)) + geom_ribbon(aes(ymin = trB.lwr,ymax = trB.upr, fill = degree), alpha = 0.2,linetype=2) + ylab('Pre-post Difference of\n Total Social Screen Time') + xlab("The amount of apps")+ggtitle('The effect of intervention B,\nadjusting for the median age (23),median procrastination(34.5), \nand female ')+theme(plot.title = element_text(hjust = 0.5))+geom_hline(yintercept=0, linetype="dashed", 
                color = "blue", size=1)
```

```{r}
# model 2 

procas =12:68 - 34.5
sex = c(0,1)
pro_sex =merge(data.frame(procrastination = procas), data.frame(sex = sex), by = NULL)
pro_sex['apps'] = 0
pro_sex['degree'] = 0
pro_sex['age_centered'] = 0

pre = predict(fit,pro_sex, interval = 'confidence',se.fit = T)
fit_conint = pre[c("trB.pred", "trB.se.fit","trB.lwr","trB.upr")]

pro_sex = cbind(pro_sex, fit_conint)
pro_sex['z'] = pro_sex$trB.pred /pro_sex$trB.se.fit
pro_sex['pvalue'] = pt(abs(pro_sex$z), df = 27,lower.tail = FALSE) *2
pro_sex$sex = as.factor(pro_sex$sex)
pro_sex$sex = ifelse(pro_sex$sex ==0, 'Female','Male')
plt5 = pro_sex %>% ggplot(aes(x = procrastination+34.5,y =trB.pred,group = sex)) + geom_line(aes(color = sex)) + geom_ribbon(aes(ymin = trB.lwr,ymax =trB.upr, fill = sex), alpha = 0.2,linetype=2) + ylab('Pre-post Difference of\n Total Social Screen Time') + xlab("Procrastination value")+ggtitle('The effect of intervention B,\nadjusting for the median age (23), the median number of apps,\n and Non-US degree')+theme(plot.title = element_text(hjust = 0.5))+geom_hline(yintercept=0, linetype="dashed", 
                color = "blue", size=1)
```

```{r}
# model2 
# apps_sex
apps =1:32 - 4
sex = c(0,1)
age = 21:30 -23
apps_sex =merge(data.frame(apps= apps), data.frame(sex = sex), by = NULL)
apps_sex['age_centered'] = 0
apps_sex['procrastination'] = 0
apps_sex['degree'] = 0

pre = predict(fit,apps_sex, interval = 'confidence',se.fit = T)
fit_conint = pre[c("trB.pred", "trB.se.fit","trB.lwr","trB.upr")]

apps_sex = cbind(apps_sex, fit_conint)
apps_sex['z'] = apps_sex$trB.pred /apps_sex$trB.se.fit
apps_sex['pvalue'] = pt(abs(apps_sex$z), df = 27,lower.tail = FALSE) *2
apps_sex$sex = as.factor(apps_sex$sex)
apps_sex$sex = ifelse(apps_sex$sex ==0, 'Female','Male')
plt6 = apps_sex %>% ggplot(aes(x = apps+4,y = trB.pred,group = sex)) + geom_line(aes(color = sex)) + geom_ribbon(aes(ymin = trB.lwr,ymax = trB.upr, fill = sex), alpha = 0.2,linetype=2) + ylab('Pre-post Difference of\n Total Social Screen Time') + xlab("The amount of apps")+ggtitle('The effect of intervention B,\nadjusting for the median age (23),median procrastination(34.5), \nand Non-US degree ')+theme(plot.title = element_text(hjust = 0.5))+geom_hline(yintercept=0, linetype="dashed", 
                color = "blue", size=1)
```

```{r}
ggarrange(plt4,plt5,plt6,labels = c('A','B','C'),ncol =2, nrow=2)
```







```{r}
library(ggplot2)
date = seq.Date(from = as.Date('2022-03-01'), to = as.Date('2022-03-30'), by = 'days')
tt =c()
for(i in c(1:30)){
  tt[i] = mean(df_sc$Tot.Scr.Time[df_sc$Time==i], na.rm = T)
}
phase = c(rep('P', 14), rep('A', 8), rep('B', 8))
dd = data.frame(soc_t = tt, date = date, phase = phase)
ggplot(dd, aes(x = date, y = soc_t, group = phase)) + geom_line(aes(color = phase)) + 
  geom_point() + xlab('date') + ylab('social app usage time') + 
  theme(axis.text.x = element_text(face = 'bold', angle = 45)) + 
  labs(title = 'mean social total time ~ date')

```


